Sampling Strategies in Decisions from Experience

### 2022-05-17 manuscript.Rmd
Using latex code for figures to add figure notes

```{r sampling-paradigm, fig.cap="(ref:sampling-paradigm)"}
knitr::include_graphics(path = "manuscript_files/sampling-paradigm.png")
```

@@

1. *Lack of formal modeling/unstated theoretical commitments:* The authors offer a verbal description of their theoretical claim that sampling strategies are systematically linked to decision strategies.
Yet, they do not provide a formal specification or computational implementation of their theory.
Such a lack of formal, mathematical or computational modeling can, among others, hide gaps and inconsistencies in the theory [@guestHowComputationalModeling2021; @vanrooijPsychologicalModelsTheir2022].
For instance, although the proposed links between sampling and decision strategies are used to explain the (non)occurrence of an as-if underweighting of rare outcomes pattern, no formal and complete accounts of the potential choice-generating mechanisms---which must contain the proposed links---are provided.
One key characteristic of the sampling paradigm is that people can freely decide when to stop sampling.
Thus, in order to be considered complete, models aiming to explain how the mind exercises the capacity of making DFE in the sampling paradigm must account for stopping.
Theoretical frameworks that do so, e.g., sequential sampling models [e.g., @markantModelingChoiceSearch2015], may, however, make themselves assumptions about the decision-making process that constrain how such a proposed link between sampling and decision strategies can be   
Failing to explicitly spell out theoretical commitments and/or to formally model the decision-making process

>>>>

\begin{figure}[t]
\caption{Possible Sampling and Decision Strategies in the Sampling Paradigm and Their Impact on the Final Choice}
\includegraphics{manuscript_files/sampling-paradigm} \label{fig:sampling-paradigm}
\raggedright \textit{Note.} Add note
\end{figure}

@@

1. *Lack of formal modeling/unstated theoretical commitments:*
The authors offer a verbal description of their theoretical claim that sampling strategies are systematically linked to decision strategies, but do not provide a formal specification or computational implementation of their claim.
Moreover, although the proposed links between sampling and decision strategies are used to "explain" the (non)occurrence of an as-if underweighting of rare outcomes pattern, no formal and complete accounts of the potential choice-generating mechanisms---which must contain the proposed links---are provided.
Such a lack of formal, mathematical or computational modeling can, among others, hide gaps and inconsistencies in the theory [@guestHowComputationalModeling2021; @vanrooijPsychologicalModelsTheir2022].
For instance, one key characteristic of the sampling paradigm is that people can freely decide when to stop sampling.
Thus, in order to be considered complete, models aiming to explain how the mind exercises the capacity of making DFE in the sampling paradigm must account for stopping.
Theoretical frameworks that do so, e.g., sequential sampling models [e.g., @markantModelingChoiceSearch2015], make themselves assumptions about the decision-making process that may constrain how the a proposed link between sampling and decision strategies can be specified.
Failing to explicitly spell out theoretical commitments and/or to formally model the decision-making process can later on
